\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{hyperref} % For hyperlinks

\title{Reflection Report for \progname{} (IPCS)}
\author{\authname}
\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\section{Changes in Response to Feedback}

Feedback from reviewers, including domain experts, secondary reviewers, and the instructor, has been diligently incorporated into the documentation.

\subsection{SRS}

The Software Requirements Specification (SRS) has been meticulously updated based on reviewer feedback. The changes made are summarized below:

\begin{itemize}
    \item Addition of theoretical underpinnings for the definition of underlying acceleration.
    \item Inclusion of derivations for two general definitions.
    \item Consolidation of two instance models into a single one.
    \item Enhancement of specificity and completeness in both functional and non-functional requirements.
\end{itemize}

For a detailed overview of these modifications, refer to the pull request [\href{https://github.com/mirzaim/ipcs/pull/29}{\#29}].

\subsection{VnV Plan}

The Verification and Validation (VnV) Plan has been updated to address reviewer comments effectively. Key changes include:

\begin{itemize}
    \item Addition of supplementary tests for integration testing.
    \item Clarification on scenarios where a test should fail.
    \item Removal of test \texttt{test-vis-3}.
\end{itemize}

For a comprehensive view of these adjustments, consult the pull request [\href{https://github.com/mirzaim/ipcs/pull/30}{\#30}].

\subsection{Design and Design Documentation}

The design and accompanying documentation have been refined to align with reviewer recommendations. Notable enhancements comprise:

\begin{itemize}
    \item Introduction of a main module to oversee the entire system.
    \item Creation of a Manager abstract class, from which GUI and File Output modules inherit.
    \item Rectification of input and output types in various modules.
    \item Consistent naming conventions across files.
\end{itemize}

To delve deeper into these changes, review the pull request [\href{https://github.com/mirzaim/ipcs/pull/34}{\#34}].

\section{Design Iteration}

The journey from the initial design to the final implementation witnessed significant evolution and refinement. Two major iterations stand out:

\begin{enumerate}
    \item Addition of the constraint $\frac{m}{5} \leq m \leq M$: Although initially deemed unnecessary, this constraint proved crucial for the proper functioning of controller hyperparameters.
    \item Refinement of the simulation formula: Initially neglecting torque and friction in the simulation, we adopted a formula discovered in a \href{https://github.com/jitendra825/Inverted-Pendulum-Simulink}{Matlab code} for simulating the inverted pendulum. This decision facilitated easier implementation by translating the Matlab code into Python.
\end{enumerate}

\end{document}
